---
title: "Rstudio::conf 2020"
subtitle: "😏<br/> powered by xaringan"
author: "Amy Tzu-Yu Chen"
iate: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
---
background-image: url(https://pbs.twimg.com/media/EPuu5-AX4AATqFy?format=jpg&name=medium)
background-position: 30% 30%
class: center, bottom, inverse

## R-Ladies Photo

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)


```


---

# RMarkdown

- Now you can use Rmarkdown to produce (almost) any type of documents. You can even reuse them easily

--
```{r eval=FALSE, tidy=FALSE}
library(rmarkdown) # Docs
library(xaringan)  # Slides
library(blogdown)  # Blogs or simple website
library(pkgdown)   # R package website
library(bookdown)  # Write a book
```

--

--
.footnote[
[1] Rob Hyndman had a talk on Rmd. He uses Rmarkdown for everything except writing emails. Has template R packages etc.

[2] Yihui had a cool demo on how changing 1-5 lines can change one single Rmd into 14 different format

[3] Show infinite moon reader

[4] Show examples
]

---

# Highcharter

* not free for commercial use

---
# Common New Tools for Pkg Dev
```{r eval=FALSE, tidy=FALSE}
library(usethis)   # Set up stuff that you can't ever remember
library(roxygen2)  # Documentation
library(testthat)  # Write tests
library(devtools)  # Iterate and develop
library(remotes)   # Install github dependencies
```

---

# ggplot2

- The general trend: encourage people to build their own extensions instead of contributing back to ggplot2. 

- Upcoming release of 4.0

- Focus on faster rendering of plots

--

- ggproto: basically build your own gg class

---

# funneljoin

- https://github.com/robinsones/funneljoin

```{r eval=FALSE, tidy=FALSE}
landed %>%
  after_inner_join(registered, 
                   by_user = "user_id",
                   by_time = "timestamp",
                   type = "first-firstafter",
                   suffix = c("_landed", "_registered"))
#> # A tibble: 5 x 3
#>   user_id timestamp_landed timestamp_registered
#>     <dbl> <date>           <date>              
#> 1       1 2018-07-01       2018-07-02          
#> 2       4 2018-07-01       2018-07-02          
#> 3       3 2018-07-02       2018-07-02          
#> 4       6 2018-07-07       2018-07-10          
#> 5       5 2018-07-10       2018-07-11
```


---

# library(later)

- Asynchronous programming came up a lot. Partly due to popularity of shiny.

- Schedule an R function or formula to run after a specified period of time.

- Similar to JavaScript's setTimeout function. 

```{r eval=FALSE, tidy=FALSE}
later::later(function() {
  summary(mtcars)
}, 5)
```

.footnote[[*] Not really. See next page.]

---

# arrow

- https://enpiar.com/talks/rstudio-conf-2020/#12

---

# library(future)

- Unifying R parallel solutions across platforms without changing much on existing code

- Page 6-9


- https://tinyurl.com/u75nx3a
---

class: center, middle

# Thanks!

Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).
